### 2015-08-15 writing/SNLI paper/corpus.tex
VG citation.

For the premises, we used captions from the Flickr30k corpus \cite{hodoshimage}, a collection of approximately 160k captions (corresponding to about 30k images) collected in an earlier crowdsourced effort.\footnote{
We additionally include about 4k sentence pairs from a pilot study in which the premise sentences were instead drawn from the VisualGenome corpus (under construction). These examples appear only in the training set, and have pair identifiers prefixed with \texttt{vg} in the corpus.
 } % TODO: Insert citation.
The captions were not authored by the photographers who took the source images, and they tend to contain relatively literal scene descriptions that are suited to our approach, rather than those typically associated with personal photographs (as in their example: \word{Our trip to the Olympic Peninsula}). In order to ensure that the label for each sentence pair can be recovered solely based on the available text, we did not use the images at all during corpus collection.

>>>>

For the premises, we used captions from the Flickr30k corpus \cite{hodoshimage}, a collection of approximately 160k captions (corresponding to about 30k images) collected in an earlier crowdsourced effort.\footnote{
We additionally include about 4k sentence pairs from a pilot study in which the premise sentences were instead drawn from the VisualGenome corpus (under construction; \texttt{\href{https://visualgenome.org/}{visualgenome.org}}). These examples appear only in the training set, and have pair identifiers prefixed with \texttt{vg} in our corpus.
 } % TODO: Insert citation.
The captions were not authored by the photographers who took the source images, and they tend to contain relatively literal scene descriptions that are suited to our approach, rather than those typically associated with personal photographs (as in their example: \word{Our trip to the Olympic Peninsula}). In order to ensure that the label for each sentence pair can be recovered solely based on the available text, we did not use the images at all during corpus collection.
